Point transect distance sampling in inlabru

### 2019-08-01 paper.tex
case study getting there

Excursion sets can be estimated using...  [[summarise Bolin paper here]]

@@

Another key aim of performing distance sampling surveys is to estimate the abundance of the population of interest.

\begin{figure}
	\includegraphics[scale=0.6]{figures/realized_abundance_posterior.png}
	\caption{Posterior of realized abundance}
	\label{fig:realized-abundance-posterior}
\end{figure}

\begin{figure}
	\includegraphics[scale=0.6]{figures/realized_abundance_vs_exp.png}
\end{figure}

@@

>>>>

Excursion sets can be estimated by considering increasing candidate sets $D$ and a sequential integration scheme to estimate probabilities.  An implementation is available in the \texttt{excursions} package available through the Comprehensive R Archive Network.

@@

Another key aim of performing distance sampling surveys is to estimate the abundance of the population of interest.  By specifying our spatial model as a log-Gaussian Cox process, the intensity is a $random field$.  Let $n$ denote the abundance of the population within the region of interest and $N$ its corresponding random variable within our Bayesian framework.  Integrating the mean of the random field provides a point estimate for the abundance, which we term the expected abundance (where the term expected comes from the fact this value is the rate parameter in the Poisson distribution which $N$ follows). Here we demonstrate the importance of considering the full posterior for $N$ which we call the \textit{realized} abundance.

Let $\Lambda = \int_{\Omega}\lambda(s)\mathrm{d}s$. Note that $\Lambda$ is a random variable and the integral of $\mathbb{E}[\lambda(s)]$ is equivalent to $\mathbb{E}(\Lambda)$ by Fubini's theorem.  As we mentioned above, this is the most sensible point estimate for the abundance.  We estimate the posterior $\pi(N | \Lambda)$ by a monte-carlo method.  Taking $m$ monte-carlo samples of the posterior intensity field $\lambda_1, \ldots, \lambda_m$ with corresponding expected abundance estimates $\Lambda_i = \int \lambda_i(s)\mathrm{d}s$ we estimate the posterior for the abundance as $\pi(N | \Lambda) \approx 1 / m \sum_{i=1}^m \pi (N | \Lambda = \Lambda_i)$. This is well defined since $\pi(N | \Lambda = \Lambda_i) = \text{Poisson}(N, \Lambda_i)$. \autoref{fig:realized-abundance-posterior} shows the approximate posterior for $N$ with $m = 20,000$.

For reference \autoref{fig:realized-abundance-comparison} shows a single Poisson PMF with rate parameter equal to the expected abundance.

\begin{figure}
	\includegraphics[scale=0.6]{figures/realized_abundance_posterior.png}
	\caption{Posterior of realized abundance.  The blue line marks the expected abundance}
	\label{fig:realized-abundance-posterior}
\end{figure}

\begin{figure}
	\includegraphics[scale=0.6]{figures/realized_abundance_vs_exp.png}
	\caption{Solid:  Posterior of realized abundance.  Dashed:  Poisson PMF with rate parameter $\mathbb{E}[\Lambda]$}
	\label{fig:realized-abundance-comparison}
\end{figure}

@@

TODO HERE:  Something about how this is all a one-stage model and all these plots are based on sampling from the joint posterior of all parameters.  As such all plots can be viewed as incorporating the uncertainty from the detection model.  This is a lovely and natural way to present results and an advantage of having a joint model.  I'm not sure varprop can do this?
